\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% For custom spacing
\usepackage{setspace}

% For multicolumn layout
\usepackage{multicol}

% Set applicant's personal data for header
\name{Mykola Ponych}
\address{Europe}
\contacts{Software Engineer \linebreak +380959402560 \linebreak n.ponich@gmail.com}

\begin{document}

% Print the header
\makeheader

% Print the content
\begin{cvsection}{Work Experience}
    \begin{cvsubsection}{Software Engineer}{LTD Nayax, Odesa}{Feb 2021 - Present}
        \begin{itemize}
            \item Developed a cloud-based retail system for document management and record-keeping.
            \item Started as a frontend developer, then managed microservices for frontend integration with AWS.
            \item Responsible for software updates, dependencies, and packages.
            \item Technologies: TypeScript, Angular, NestJS, PHP, C\#, AWS.
        \end{itemize}
    \end{cvsubsection}
    
    \begin{cvsubsection}{Full Stack Developer}{Khaet Digital GmbH, Berlin}{May 2020 - Feb 2021}
        \begin{itemize}
            \item Led the development of an internal system for creditworthiness assessment and credit product recommendations.
            \item Optimized existing solutions and participated in architectural decision-making.
            \item Technologies: PHP, JavaScript, C\#, AWS.
        \end{itemize}
    \end{cvsubsection}
    
    \begin{cvsubsection}{Full Stack Developer}{LTD GeekGroup, Odesa}{Mar 2018 - May 2020}
        \begin{itemize}
            \item Participated in the development of an internal system for organizing meetings and conferences in the medical logistics sector.
            \item Technologies: C\#, ASP.NET Core, .NET Framework, PHP, Angular, Sencha Ext JS.
        \end{itemize}
    \end{cvsubsection}
    
    \begin{cvsubsection}{Full Stack Developer}{LTD CRMOZ, Kyiv}{Mar 2016 - Mar 2018}
        \begin{itemize}
            \item Lead developer for business process automation in a real estate company.
            \item Developed a bidirectional data synchronization system for client data with CRM and sales funnel automation tools.
            \item Technologies: PHP (Laravel, Symfony), JavaScript (Vue), MySQL, PostgreSQL.
        \end{itemize}
    \end{cvsubsection}
    
    \begin{cvsubsection}{Full Stack Developer}{Ltd Yugo-Web, Saint Petersburg}{Aug 2014 - Mar 2016}
        \begin{itemize}
            \item Worked in a startup focused on creating business websites, online stores, and sales funnel automation.
            \item Integrated third-party services (Yandex, marketplaces, mailing, analytics).
            \item Technologies: PHP (CodeIgniter, Laravel, WordPress), JavaScript (Node.js, jQuery), MySQL, PostgreSQL, SQLite, Bootstrap.
        \end{itemize}
    \end{cvsubsection}
\end{cvsection}

\begin{cvsection}{Skills and Languages}
    \begin{cvsubsection}{}{}{}
        \begin{multicols}{2}
            \textbf{Skills:}
            \begin{itemize}
                \setlength{\leftmargin}{1em}
                \item JavaScript, Angular, Vue.js, eslint/prettier/npm
                \item AWS, Google cloud, Git, Docker
                \item PHP, C\#, Python
                \item Linux, Kubernetes, CI/CD pipelines, VM
                \item Version control systems and technical documentation, OpenAPI
            \end{itemize}
            
            \columnbreak
            
            \textbf{Languages:}
            \begin{itemize}
                \item Ukrainian (Native)
                \item Russian (Native)
                \item English (Intermediate)
            \end{itemize}
        \end{multicols}
    \end{cvsubsection}
\end{cvsection}

\begin{cvsection}{Education}
    \begin{cvsubsection}{Associate Degree}{Kyiv Vocational College, Kyiv}{Sep 2006 - Jun 2009}
        Attended from 2007 to 2009, earned a technical specialist degree in computer technology. Associate Degree in Computer Technology.
    \end{cvsubsection}
\end{cvsection}

\begin{cvsection}{Achievements}
    \begin{cvsubsection}{}{}{}
        \begin{itemize}
            \item Modularized core application components into packages, accelerating project development and enabling reuse of essential components.
            \item Enhanced build process by optimizing packaging, significantly improving build speed.
            \item Integrated AI solutions for documentation assistance and system navigation with search features.
            \item Implemented AI-based image generation for product cards.
            \item Designed and maintained AWS integration within a microservices architecture.
            \item Developed clean, efficient APIs.
        \end{itemize}
    \end{cvsubsection}
\end{cvsection}

\begin{cvsection}{About Me}
    \begin{cvsubsection}{}{}{}
        I am 33 years old and from Ukraine. Due to recent events, I had to leave my city, and I am now looking for a new place to call home, along with new friends and employment opportunities. I am eager to find an employer where I can contribute effectively, engage in interesting projects, and work within a supportive team.
        
        \begin{itemize}
            \item Open to remote work and full-time office positions
            \item Considering relocation offers
            \item Experienced Full Stack Developer with extensive sector experience in e-commerce, B2B, B2P, real estate, medical logistics, banking, and retail
            \item Proficient in Linux, AWS, Docker, Kubernetes, with strong experience in version control and documentation
        \end{itemize}
    \end{cvsubsection}
\end{cvsection}

\begin{cvsection}{Additional Information}
    \begin{cvsubsection}{}{}{}
        \begin{itemize}
            \item GitHub: https://github.com/ponich
            \item LinkedIn: https://www.linkedin.com/in/ponich
            \item Interests: Reading fantasy novels, Ice skating, camping, Interest in history and computer science
            \item References available upon request
        \end{itemize}
    \end{cvsubsection}
\end{cvsection}

\end{document}